### 2021-02-17 tarea_base_enigh/01-script.Rmd
preliminar

A<-data%>%filter(est_socio==1 & est_socio==2)
B<-data%>%filter(est_socio==3 & est_socio==4)

@@

l2<-ggplot(B, aes(log(alimentos),log(leche)))+geom_point() + theme(text = element_text(size=10), panel.background = element_rect(fill = "lightblue"),axis.title.x = element_blank()) +  labs(y="log(gasto en alimentos)", x = "log(gasto en leche)")+ ggtitle("Estrato alto")+
  stat_smooth(aes(y = log(leche)),method = "lm", size = 1,color = "yellow",se=F) +
  stat_smooth(aes(y = log(leche)),method = "lm", formula = y ~ x + I(x^2), size = 1, color = "red",se=F)+ xlim(4, 13) + ylim(3,10)

ggarrange(
 l1,l2,l3,l4, labels = c("A", "B"),
  common.legend = TRUE, legend = "bottom"
  )

@@

l2<-ggplot(B, aes(log(alimentos),log(huevo)))+geom_point() + theme(text = element_text(size=10), panel.background = element_rect(fill = "lightblue"),axis.title.x = element_blank()) +  labs(y="log(gasto en alimentos)", x = "log(gasto en huevo)")+ ggtitle("Estrato alto")+
  stat_smooth(aes(y = log(huevo)),method = "lm", size = 1,color = "yellow",se=F) +
  stat_smooth(aes(y = log(huevo)),method = "lm", formula = y ~ x + I(x^2), size = 1, color = "red",se=F)+ xlim(4, 13) + ylim(3,10)

ggarrange(
 l1,l2,l3,l4, labels = c("A", "B"),
  common.legend = TRUE, legend = "bottom"
  )

>>>>

A<-data%>%filter(est_socio==1)
B<-data%>%filter(est_socio==2)
C<-data%>%filter(est_socio==3)
D<-data%>%filter(est_socio==4)

@@

l2<-ggplot(B, aes(log(alimentos),log(leche)))+geom_point() + theme(text = element_text(size=10), panel.background = element_rect(fill = "lightblue"),axis.title.x = element_blank()) +  labs(y="log(gasto en alimentos)", x = "log(gasto en leche)")+ ggtitle("Estrato medio bajo")+
  stat_smooth(aes(y = log(leche)),method = "lm", size = 1,color = "yellow",se=F) +
  stat_smooth(aes(y = log(leche)),method = "lm", formula = y ~ x + I(x^2), size = 1, color = "red",se=F)+ xlim(4, 13) + ylim(3,10)

l3<-ggplot(C, aes(log(alimentos),log(leche)))+geom_point() + theme(text = element_text(size=10), panel.background = element_rect(fill = "lightblue"),axis.title.x = element_blank()) +  labs(y="log(gasto en alimentos)", x = "log(gasto en leche)")+ ggtitle("Estrato medio alto")+
  stat_smooth(aes(y = log(leche)),method = "lm", size = 1,color = "yellow",se=F) +
  stat_smooth(aes(y = log(leche)),method = "lm", formula = y ~ x + I(x^2), size = 1, color = "red",se=F)+ xlim(4, 13) + ylim(3,10)

l4<-ggplot(D, aes(log(alimentos),log(leche)))+geom_point() + theme(text = element_text(size=10), panel.background = element_rect(fill = "lightblue"),axis.title.x = element_blank()) +  labs(y="log(gasto en alimentos)", x = "log(gasto en leche)")+ ggtitle("Estrato alto")+
  stat_smooth(aes(y = log(leche)),method = "lm", size = 1,color = "yellow",se=F) +
  stat_smooth(aes(y = log(leche)),method = "lm", formula = y ~ x + I(x^2), size = 1, color = "red",se=F)+ xlim(4, 13) + ylim(3,10)
ggarrange(
 l1,l2,l3,l4, labels = c("A", "B","C","D"),
  common.legend = TRUE, legend = "bottom"
  )

@@

l2<-ggplot(B, aes(log(alimentos),log(huevo)))+geom_point() + theme(text = element_text(size=10), panel.background = element_rect(fill = "lightblue"),axis.title.x = element_blank()) +  labs(y="log(gasto en alimentos)", x = "log(gasto en huevo)")+ ggtitle("Estrato medio bajo")+
  stat_smooth(aes(y = log(huevo)),method = "lm", size = 1,color = "yellow",se=F) +
  stat_smooth(aes(y = log(huevo)),method = "lm", formula = y ~ x + I(x^2), size = 1, color = "red",se=F)+ xlim(4, 13) + ylim(3,10)

l3<-ggplot(B, aes(log(alimentos),log(huevo)))+geom_point() + theme(text = element_text(size=10), panel.background = element_rect(fill = "lightblue"),axis.title.x = element_blank()) +  labs(y="log(gasto en alimentos)", x = "log(gasto en huevo)")+ ggtitle("Estrato medio alto")+
  stat_smooth(aes(y = log(huevo)),method = "lm", size = 1,color = "yellow",se=F) +
  stat_smooth(aes(y = log(huevo)),method = "lm", formula = y ~ x + I(x^2), size = 1, color = "red",se=F)+ xlim(4, 13) + ylim(3,10)

l4<-ggplot(B, aes(log(alimentos),log(huevo)))+geom_point() + theme(text = element_text(size=10), panel.background = element_rect(fill = "lightblue"),axis.title.x = element_blank()) +  labs(y="log(gasto en alimentos)", x = "log(gasto en huevo)")+ ggtitle("Estrato alto")+
  stat_smooth(aes(y = log(huevo)),method = "lm", size = 1,color = "yellow",se=F) +
  stat_smooth(aes(y = log(huevo)),method = "lm", formula = y ~ x + I(x^2), size = 1, color = "red",se=F)+ xlim(4, 13) + ylim(3,10)

ggarrange(
 l1,l2,l3,l4, labels = c("A", "B","C","D"),
  common.legend = TRUE, legend = "bottom"
  )
